% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\addtolength{\textheight}{1.6in}
\addtolength{\voffset }{-.25in}
\addtolength{\oddsidemargin }{-.25in}

\begin{document}

\name{\Large Kyle W. Rader}
% \address used twice to have two lines of address
\address{23714 NE 61st Street, Redmond, Wa, 98053}
\address{(425) 241-7977 \hspace{13mm} kyle.rader@ieee.org}
 
\begin{resume}
 
\section{OBJECTIVE}       I learn as much as I can while innovating software solutions for complex and interesting problems. I love what I do and I'm comfortable not knowing how to solve the puzzle in front of me, but I'm confident I will.
 
 
\section{EDUCATION}   Graduating June 2014 with a {\sl B.S.} in Computer Science and minors in Math and Embedded Systems from 
			      Western Washington University, Bellingham, Wa ({\sl gpa: 3.44/4.0}).
 
 
\section{LANGUAGES}
	\begin{table}[h]
		\begin{tabular}{ l l l }
			{\sl Experienced}: \\
			C\#, C, {\LaTeX}, Ruby, Javascript, PHP, HTML
					
		\end{tabular}
 	\end{table}

\section{EXPERIENCE}

		{\sl Director of Engineering} \hfill December 2013 - Present \\
                	Uzility, Bellingham, Wa
               	 \begin{itemize}  \itemsep -2pt
                		\item Developing web and mobile based tools for agile software development and process management.  
                		\item Practicing lean start-up methodology and agile software developement. 
                		\item Develop both front end UI and back end web services using Zurb's Foundation framework, PHP, HTML, Javascript, CSS, and MySQL.  
                	\end{itemize}

		%{\sl Project Lead} \hfill October 2013 - Present \\
                	%HouseWare LLC, Bellingham, Wa
               	 %\begin{itemize}  \itemsep -2pt
                	%	\item Managing a team of students (including myself) from WWU to rapidly develop a prototype house optimization and utilities system.
                	%	\item Managed a team at Startup Bellingham Weekend pitching and launching HouseWare.
                	%\end{itemize}

                	{\sl Lab TA} \hfill        Fall 2011, Spring 2012, Fall 2013, Spring 2014 \\
                	WWU, Computer Science Dept, Intro to Robotics
                  	\begin{itemize}
                   		\item Organize, run and grade labs.
                   		\item Give supplementary and engaging mini lectures in lab.
			\item Hold extra lab office hours.  
                   	\end{itemize}

		{\sl Software Engineer} \hfill Spring 2012 - spring 2014 \\
                	Brer Technical Inc, Bellingham, Wa
                	\begin{itemize}  \itemsep -2pt
                		\item Develop .NET API's for serial communication with motor controllers and mega ohm meters.
                		\item Business management system centered on our MFI test procedure.
			\item Event based testing interface with real time data collection and visualization.  
               	 \end{itemize}
 
		{\sl Software Developer} \hfill June 2013 - January 2014 \\
                	Logos Bible Software, Bellingham, Wa
               	 \begin{itemize}  \itemsep -2pt
                		\item Developed and maintained an internal Ruby on Rails site housing database and server management tools. 
	     		\item Tools include RabbitMQ message replay, MySQL cluster dashboard, server patch dashboard and schema migration dashboard.
                	\end{itemize}

                	{\sl Research Assistant} \hfill            Summer 2011 - Spring 2013 \\
                	WWU, Math Dept, NSF grant for geometric tomography.
                 	\begin{itemize}  \itemsep -2pt
                 		\item Data processing, GUI design and algorithm implementation in Matlab.
                 	\end{itemize} 

		%{\sl Stunt Actor} \hfill Summer 2010 \\
		%Wing-It Productions, Seattle, Wa
		%\begin{itemize}
		%	\item Live audience performances
		%\end{itemize}

		{\sl Taekwondo Instructor} \hfill Sept 2005 - Sept 2007 \\
		Hwangs Taekwondo, Redmond, Wa
		\begin{itemize}
			\item Instructor of the year 2007.
		\end{itemize}

	References provided upon request.
	
\section{AWARDS}
	\begin{itemize} \itemsep -1pt
		\item Technology Alliance Group: Technology Leader of Tomorrow, Dec 2013
		\item WWU Computer Science Citizenship Scholarship, 2013
		\item Logos Bible Software Scholarship, 2012
		\item Dealer Information Systems Scholarship, 2011
	\end{itemize}
\newpage
 
\section{VOLUNTEER \\ SERVICE}
		\begin{itemize} \itemsep -1pt
			\item Jr. Supervisor Bellingham A.I. and Robotics Society.  Taught kids programming through robotics. (Winter 2011 - Winter 2013)
			\item WWU ACM mentor.  Tutor students in intro level computer science courses.  (Ongoing)
		\end{itemize}

\section{EXTRA-CURRICULAR \\ ACTIVITIES} 
	\begin{itemize} \itemsep -1pt
	\item Activities Coordinator WWU ACM (Spring 2013 - present)
	\item CCDC/ Cyber Defense Club ({\sl Fall 2012 - Spring 2013)})
	\item President: Western Student Robotics Club ({\sl Fall 2010 - Spring 2012})
 	\item Vice President: Institute of Electrical and Electronics Engineers WWU Chapter ({\sl Fall 2011 -Spring 2012})
	\item Associated Students Inter Club Council: Academic Representative ({\sl Fall 2010 - Spring 2011})
	\end{itemize}
\end{resume}
\end{document}







