% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\addtolength{\textheight}{2in}
\addtolength{\textwidth}{.5in}
\addtolength{\voffset }{-.5in}
\addtolength{\oddsidemargin }{-.5in}

\begin{document}

\name{\Large Rainier K Harvey}
% \address used twice to have two lines of address
\address{1034 24th Street Apt 5 Bellingham, WA 98225}
\address{(360) 931-3237 rainierharvey@gmail.com, rainierharvey.me}
 
\begin{resume}
 
\section{EDUCATION}   Western Washington University, Bellingham, Wa ({\sl gpa: 3.2/4.0}).\\
			     {\sl B.S.} in Computer Science (June 2017). Minor in Mathematics\\
			      Class of 2017: {\sl M.S.} in Computer Science.
			      
 {\sl Languages} 
	\begin{table}[h]
		\begin{tabular}{l l l}
			Python, JavaScript, Java, CSS, HTML, C\#	
		\end{tabular}
 	\end{table}

\section{EXPERIENCE}

		{\sl Lifeguard} \hfill June 2010 - September 2014 \\
                	Vancouver Parks and Recreation, Vancouver, Wa
               	 \begin{itemize}  \itemsep -2pt
                		\item Trained under Elis and Associates Lifeguarding for certification and maintained certification.
                		\item CPR, AED, emergency equiment application and first aid training.
                		\item Monitor indoor swimming area, interactions with customers.
						\item Train new employees in emergency response and general conduct.
                	\end{itemize}

        {\sl WSI Swim Instructor} \hfill June 2010 - September 2014 \\
                	Vancouver Parks and Recreation, Vancouver, Wa
                  	\begin{itemize} \itemsep -2pt
                   		\item Plan and run swim lessons.
			\item critque and grade students, communicate with parents.
			\item Train new employees in teaching, communication with parents and students.
                   	\end{itemize}

\section{PROJECTS}
	{\sl } \hfill https://github.com/euranium \\ 					
	\begin{itemize} \itemsep -1pt
		\item Designed, implemented specialized restaurant selector in node.js with LESS, express, backbone, ejs
		\item Remake classic tic-tac-toe game with several dynamic variants with Angular.js, css, html
		\item Design dynamic and intelligent task manager website, Taskameleon, with backbone.js, jQuery, css, html
		\item Create dynamic substitution web site for Vancouver Parks and Recreation Aquatics deparment
		\item Back end work with Django web framework, node.js with express.js, C\# .NET, Sqlite, postgesql, nginx 
		\item Front end work with JavaScript, Angular.js, Backbone.js, jQuery, Twitter Bootstrap, html, css, ejs, jade 
		\item Computer AI playing tic-tac-toe in Java
	\end{itemize}

\section{AWARDS}
	\begin{itemize} \itemsep -1pt
		\item International Baccalaurete Diploma
		\item Swim team captain, most valuable athlete
	\end{itemize}
 
\section{VOLUNTEER \\ SERVICE}
		\begin{itemize} \itemsep -1pt
			\item Humane Society, spring 2012
			\item Boy Scouts of America, 2007-2012
		\end{itemize}

\section{EXTRA-CURRICULAR \\ ACTIVITIES} 
	\begin{itemize} \itemsep -1pt
	\item Association for Computing Machinery national member
	\item Association for Women in Computer Science member
	\item Invent Coworking Startup Challenge, WWU Hackathon
	\item WWU Startup Club
	\item Mathematics problem solving club
	\item USA Swimming
	\item USA Triathalon
	\item German club
	\end{itemize}
\end{resume}
\end{document}

